Nodal Discontinuous Galerkin Method for the Euler Equations in GR

### 2018-10-31 Documents/Euler/dgEulerGR.tex
Added to dgEulerGR.tex

>>>>

So, we end up with:
\begin{equation}
    \Delta t<\text{min}\left\{\text{min}_{i}\left(\f{\ve\,\Delta V_{i}}{2\,\text{max}\left(\sqrtgm_{i\pm\f{1}{2}}\,\alpha_{i\pm\f{1}{2}}\right)}\right),\text{min}^{n}_{i}\left(\f{2\left(1-\ve\right)}{\ol{P^{kk}\,\p_{1}\,\gamma_{kk}}}\left[-\ol{S}_{1}\pm\sqrt{\ol{\gamma_{11}}\,\ol{\tau}\left(\ol{\tau}+2\,\ol{D}\right)}\right]\right)\right\}.
\end{equation}
